MLH1 data report 

### 2018-02-08 1rmd_report.rmd
new md report files uploaded

---
title: "MLH1 data report "
author: "April Peterson"
date: "August 29, 2017"
output: github_document
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
#setwd("C:/Users/alpeterson7/Documents/MLH1repo")
setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
#kable(AP_strain_table)
```

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
                              "WSB", "PWD","MSM","CAST","HMI","SPRET", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ss <- ss   + facet_wrap(~ sex, scales="free")

@@

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}
histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

@@

qq <- ggplot(highest_qual_df, aes(x = mouse, y = adj_nMLH1.foci)) + geom_boxplot(data = highest_qual_df, aes(fill = factor(strain) ) ) +  ggtitle("Cells with quality scores of 2 or 1") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
high_qual_boxplot <- qq + facet_wrap(~ sex, scales="free") #this is breaking the kniting... 
```

@@

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
ff
high_qual_boxplot
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16, 18) ]
#7, PERC. 12 CASTF, 14 HMI f , 16 SPRET f. 18 other

df_list 
o=0
i=0

for(i in 1:(length(df_list))){
 # print(i)
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
 # print(sub_mouse_means)
  #below should work -- I think I need to go througheach row of the df_list[[i]]
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

>>>>

---
title: "MLH1 data report "
author: "April Peterson"
date: "Feb 6, 2018"
output: github_document
---

```{r setup, echo=FALSE, include = FALSE}
#
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
#setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
n <- kable(AP_mouse_table)
n
```

MLH1_data <- MLH1_data %>%
  arrange(category) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

MLH1_data <- with(MLH1_data, MLH1_data[order(category),])

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
                              "WSB", "PWD","MSM","KAZ","CAST","HMI","SPRET","SPIC", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green","purple","grey1", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey" ))
ss <- ss   + facet_wrap(~ sex, scales="free")

@@

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}
#consider making distribution with quality considered...

histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

@@

#are there no KAZ cells of high quality?
qq <- ggplot(highest_qual_df, aes(x = mouse, y = adj_nMLH1.foci)) + geom_boxplot(data = highest_qual_df, aes(fill = factor(strain) ) ) +  ggtitle("Cells with quality scores of 2 or 1") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "red","yellowgreen", "green","purple", "black", "grey" ))
high_qual_boxplot <- qq + facet_wrap(~ sex, scales="free") #this is breaking the kniting... 
```

@@

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
qq
high_qual_boxplot
#not sure why order got messed up again...
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7, 12, 14,16,19, 21) ]
#7: PERC male,   12: #KAZ female! 14:CAST female 16:HMI female,19:SPIC male, 21:SPIC male

#df list, is a list of df's which were split() from BIG df by category
df_list 
o=0
i=0

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assining the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}
